Postdoctoral Researcher

### 2016-09-19 GenericCV/PostdocCSU/CV_Shih-Kai_Lin.tex
changed numubar into muon antineutrino

\section{Experience}
%\subsection{Vocational}
\cventry{2014--present}{Postdoctoral Researcher}{Colorado State University}{Fort Collins, CO}{}{Member of the NOvA and the 35-ton prototype collaboration at Fermi National Accelerator Laboratory.
\begin{itemize}
  \item Measuring $\bar{\nu}_\mu$ charged-current inclusive cross section with the NOvA near detector.
  \item Developed the control application for the LBNE calibration module for photon detector, which was used in 35-ton prototype's data taking.
  \item Photon detector R\&D and performance study.
\end{itemize}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% UH era
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cventry{2009--2014}{Research Assistant}{University of Houston}{Houston, TX}{}{Member of particle physics group and Daya Bay Reactor Neutrino Experiment. Actively participated in the muon detector system QC/QA, installation, commissioning, operation and data analysis.%\newline{}%
%Detailed achievements:%
\begin{itemize}%
  \item	Analyzed data for neutron production by cosmic ray muons.
  \item Developed a reconstruction algorithm to reconstruct the incident position and the track of cosmic ray muons.
  \item Designed and built a small resistive plate chamber for monitoring the gas composition.
  \item Experience in operating radioactive sources such as $^{137}$Cs, $^{90}$Sr and $^{60}$Co for resistive plate chamber response study.
  \item Designed and built a collimator for shielding and collimating $^{60}$Co.
%  \item Monte Carlo simulation on photoelectron production by photons and electron transport in Bakelite.
%  \item Developed a web based 3D muon event display with WebGL and MySQL technology.
%  \item During hardware installation, led a team of technicians to route 400 electronic cables from a 10m deep pool to the electronics control room in a week.
\end{itemize}}
%\cventry{}{}{}{}{aa}{
\begin{cvitemize}
  \item Monte Carlo simulation on photoelectron production by photons and electron transport in Bakelite.
  \item Developed a web based 3D muon event display with WebGL and MySQL technology.
  \item During hardware installation, led a team of technicians to route 400 electronic cables from a 10m deep pool to the electronics control room in a week.
\end{cvitemize}

>>>>

\section{Experience}
%\subsection{Vocational}
\cventry{2014--present}{Postdoctoral Researcher}{Colorado State University}{Fort Collins, CO}{}{Member of the NOvA and the 35-ton prototype collaboration at Fermi National Accelerator Laboratory.
\begin{itemize}
  \item Measuring muon antineutrino charged-current inclusive cross section with the NOvA near detector.
  \item Developed the control application for the LBNE calibration module for photon detector, which was used in 35-ton prototype's data taking.
  \item Photon detector R\&D and performance study.
\end{itemize}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% UH era
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cventry{2009--2014}{Research Assistant}{University of Houston}{Houston, TX}{}{Member of particle physics group and Daya Bay Reactor Neutrino Experiment. Actively participated in the muon detector system QC/QA, installation, commissioning, operation, and data analysis.%\newline{}%
%Detailed achievements:%
\begin{itemize}%
  \item	Analyzed data for neutron production by cosmic ray muons.
  \item Developed a reconstruction algorithm to reconstruct the incident position and the track of cosmic ray muons.
  \item Designed and built a small resistive plate chamber for monitoring the gas composition.
  \item Experience in operating radioactive sources such as $^{137}$Cs, $^{90}$Sr and $^{60}$Co for resistive plate chamber response study.
  \item Designed and built a collimator for shielding and collimating $^{60}$Co.
%  \item Monte Carlo simulation on photoelectron production by photons and electron transport in Bakelite.
%  \item Developed a web based 3D muon event display with WebGL and MySQL technology.
%  \item During hardware installation, led a team of technicians to route 400 electronic cables from a 10m deep pool to the electronics control room in a week.
\end{itemize}}
%\cventry{}{}{}{}{aa}{
\begin{cvitemize}
  \item Monte Carlo simulation on photoelectron production by photons and electron transport in Bakelite.
  \item Developed a web based 3D muon event display with WebGL and MySQL technology.
  \item During hardware installation, led a team of technicians to route 400 electronic cables from a 10m deep pool to the electronics control room in a week.
\end{cvitemize}
